\section{Testing the MCU Implementation}

This section describes the tests written in software, and the energy measurements
done with Silicon Labs' \textit{energyAware Profiler}. The software tests can be
divided into to groups, Unit tests and Demo programs.

\subsection{Unit tests}

Unit tests were developed for the non-hardware dependent code. These are
utility components which executes correctly independently of the underlying
platform. The tests were written in the CppUTest framework \ref{cpputest} and executed
on each developers own laptop.

\subsubsection{Testing the controller for ChaosM}
The controller for the \textit{ChaosM} included functions for reading and writing
to its input buffers and controlling it through the different control registers.
Integrating with the \textit{ChaosM} and its address space could prove to be a
difficult task. Thus, the processor was mocked and unit tests created during 
development of both the processor and the controller.
This made for easy changes of the controller during the ChaosM development.

\subsection{Demo Programs}

While developing the software library interfacing with the hardware using emlib
and CMSIS, small demo programs were written. These programs verify two things;
that the software runs correcly, and that the underlying hardware devices are
connected according to the specifications. This was acccomplished by running the
program on both the PCB and the development kits available at the lab.

\subsubsection{Transfer from ADC to DAC with DMA}
\paragraph{Testfile: sw/modules/adc/demo/ADD.c}

This test verifies that this pipeline is set up correctly. It confirms that the
minijacks are connected the correct GPIO ports. As the ports are the same on the
development kit\cite{efm32gg-devkit} and the project's PCB, this test has been used to verify
the PCB design and implementation.

This demo program sets up the ADC as sample source and DAC as the sample output.
DMA is used to copy from the ADC to an input buffer in the Internal RAM on the
MCU. After 64 samples, the CPU is interrupted and transfers the samples to the
output buffer. A second DMA channel copies from the output buffer to the DAC.

\subsubsection{Transfer from ADC to DAC Through FPGA Mock}
\paragraph{Testfile: sw/modules/fpga/demo/fpga.c}

This demo is a copy of the previous test with the addition of deinterleaving and
interleaving to confirm that these operations run correctly.

\subsubsection{copy-file.c}
The copy file demo sets up the MCU to read samples a wav file on a SDCard and to write
them back to the same card in a different file. It verifies that the FatFS file system
and MicroSD libraries are set up correctly and that the SD slot on the circuit board
is working.

\subsubsection{wavplayer.c}
The wavplayer demo verifies that a stream from a file on the SD card can be sent to the
DAC output source. 
