% !TEX root = ../../report.tex
\section{Assignment}

Our interpretation of the assignment..

\section{Original Assignment Text}

\subsection{Task: Construct a Multiple Program, Multiple Data}
The performance increase available from harvesting Instruction Level Parallelism
(ILP) from the serial instruction stream is limited because we have reached the
maximum power consumption that can be handled without expensive cooling
solutions [1]. Consequently, there is a significant interest in single-chip
parallel processor solutions (e.g. [2,3]). The processor cores in commercial
multi-core chips are conventional designs and therefore reasonably complex. In
this work, your task is to design a multiprocessor,Multiple Instruction,
Multiple Data streams (MIMD). A processor classified MIMD include a multiple-
instruction stream organizations[5]. Such processors can executing different
instructions, i.e. minimum 2 independent programs, on different (independent)
data.

The task also include that a suitable application is chosen to demonstrate the
processor. Your processor will be implemented on an FPGA, and you are free to
choose how to realize your MIMD computer architecture. The system should be
shown to work with a suitable application. Studying the architecture of the
Cell processor [7], or in general multi-core processors [6], can be a good
starting point. And a final tip; Keep it simple, as simple as possible, but not
simpler. Due to a large number of students this year, we will divide the work
into two independent projects: a) Performance and b) Energy efficiency. The goal
of group a) is to achieve maximum performance while group b) should try to
balance performance and energy. The reports from both groups should include an
evaluation of prototype performance and energy consumption.

\subsection{Additional Requirements}
The unit must utilize an Energymicro micro controller and a Xilinx FPGA. The
budget is 10.000 NOK, which must cover components and PCB production. The unit
design must adhere to the limits set by the course staff at any given time.
Deadlines are given in a separate time schedule.

\subsection{Evaluation}
The project is evaluated based on the project report and an oral presentation of
the work as well as a prototype demonstration. One grade will be given to the
group as a whole, unless there are significant variations in the amount of
effort put into the project.

\subsection{References}

\begin{enumerate}
	\item Olukotun and Hammond; The Future of Microprocessors; ACM Queue; 2005
\item Bell et al.; TILE64 - Processor: A 64-Core SoC with Mesh Interconnect; ISSCC; 2008
\item Kongetira et al.; Niagara: A 32-way Multithreaded Sparc Processor; IEEE MICRO; 2005
\item Wikipedia; Goodyear MPP; http://en.wikipedia.org/wiki/Goodyear\_MPP
\item M Flynn; Some Computer Organizations and Their Effectiveness; IEEE Transactions on Computers. Volume:C-21 , Issue: 9. 1972
\item Wikipedia; Multi-core processor; http://en.wikipedia.org/wiki/Multi-core
\item Wikipedia; Cell (microprocessor);http://en.wikipedia.org/wiki/Cell\_(microprocessor)
\end{enumerate}
