\chapter{Results}\label{chapter:results}

This chapter details the results from all the tests in the previous chapter. It
also details whether the system as a whole has satisfied the project assignment.

\clearpage
\section{Assignment results}

While \textit{ChaosM} was able to fully function with one pipeline in
simulation, there was insufficient time to successfully integrate it on the FPGA
chip on the system. Therefore, the actual audio processing was never
successfully tested on the system. Consequently many of the Functional
Requirement Tests (FRTs) were not tested. However, the I/O controller was
successfully tested against both the SRAM and the FPGA chip when configured as
RAM. The PCB was also thoroughly tested. Following are the testing results of
these two components.

%The below input is a subsection of the above section
\input{chapters/results/mcu-results}
%The below input is a subsection of the above section
\input{chapters/results/pcb-results}

\clearpage
\section{Test Results}
Following are the test results of the FR tests, the simulation tests of
\textit{ChaosM}, and finally the power measurement test.

\subsection{FR test results}
Following are the results of the FRs. Due to \textit{ChaosM} not being
successfully implemented, some of the FRTs have not been tested.

\paragraph{Functional requirement 1}
\textit{The audio pipelines must receive and execute different data and instruction streams.}\\
This test was not successfully tested due to the lack of an implemented \textit{ChaosM} on the FPGA chip.

\paragraph{Functional requirement 3}
\textit{The audio processor must consist of at least two audio channels.}\\
One audio pipeline, e.g. an audio channel, was successfully achieved in simulation. Again, this was not confirmed on the system due to \textit{ChaosM}'s lack of successful implementation the system.

\paragraph{Functional requirement 6}
\textit{The cores in the audio pipelines should share data with each other through a ring buffer.}\\
Again, as the above FRT, this was achieved in simulation. It was not tested on the system, and can therefore not be claimed to be achieved.

\paragraph{Functional requirement 7}
\textit{It must be possible to observe power consumption over certain components.}\\
This functional requirement was successfully achieved. With current sensors on the power supply to the MCU and FPGA chips, the results these sensors produced were as expected.

\paragraph{Functional requirement 8}
\textit{The audio system should perform real time filtering on two distinct
channels, with an audio quality of 8-bits and a frequency 44.1kHz.}\\
This FR was not achieved. For the same reasons as FRs 1, 3, 6.

\paragraph{Functional requirement 9}
\textit{The microcontroller and the audio processor should communicate via ARMs
External Bus Interface.}\\
Besides the fact that the PCB did not connect the EBI bus' data lines for the FPGA, this FR was achieved with the documented fix described in Section \ref{fixes}.

\paragraph{Functional requirement 11}
\textit{The MCU must have an SD card interface and a UART serial port.}\\
This FR was successfully achieved. The I/O controller successfully interfaced with the SD card and the UART serial port.

\paragraph{Functional requirement 12}
\textit{The board should have buttons and LEDs.}\\
With the I/O controller, this FR was tested and successfully achieved.

\paragraph{Functional requirement 13}
\textit{The system should be able to process both digital and analog signals.}\\
This FR was partially achieved. While \textit{ChaosM} was as previously mentioned never implemented successfully on the system, the I/O controller successfully implemented demonstration programs that were able to receive and process data from both analog input, the minijacks, and the digital input, the SD card.
In essence, the requirement of being able to utilize both analog and digital sources, was successfully achieved through the use of the ADC and the DAC. This was not achieved on the fully implemented system though.

%The below input is a subsection of the above section
\input{chapters/results/fpga-simulation-results}

\clearpage
\input{chapters/results/power-measurements}

%The below input is a subsection of the previous section
\input{chapters/results/energy-profiling}
