\FloatBarrier
\section{FPGA}\label{chapter:fpga}

\textit{ChaosM} consists of two audio processing pipelines, each containing four
homogenous processor cores. The processor cores are turing complete processing
units connected to constant memory, an input buffer, an output buffer, and
instruction memory. Each core exchanges data through the input/output buffers.
Data from the I/O controller is written into the input buffer of the first core, and read
back from the output buffer of the last core.

With this design, each pipeline of cores can run a set of filters, for instance
a fourier transform, a frequency filter, an inverse fourier transform, and an
effect on the audio data stream running through the audio pipelines of \textit{ChaosM}.

\input{chapters/implementation/fpga/pipelines}
\input{chapters/implementation/fpga/communication}
\input{chapters/implementation/fpga/isa}
\input{chapters/implementation/fpga/memory}
\input{chapters/implementation/fpga/core}

\subsection{Energy Efficiency}

\textit{ChaosM} is designed with a basic idea of energy efficiency. Since the different cores
in each pipeline perform different tasks, it is natural for them to finish independently of 
eachother. Therefore, \textit{ChaosM} is designed so that it is possible to turn of the individual 
cores once they finish operating. This functionality has a negible effect on the power consumption
of an FPGA and therefore doesn't affect energy efficiency on this particular system. If the
\textit{ChaosM} design was recreated in hardware on a designated chip, however, this functionality
could improve energy effieciency.

